### 2016-12-13 poster/poster.tex
added useless figure

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{tabularx}

@@

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & 26h10m & 35h25m & (TBD)\\
Train epoch & x & 6h57m & 6h35m \\
Test epoch & x & 7m45s & 24m \\
Train batch & 1s & 5s & 1s \\
Test batch & < 1s & $<$1s & < 1s \\
\end{tabular}
\egroup
\vspace{5pt}
}

@@

\textbf{Time spent in various functions}

@@

\begin{tabularx}{\textwidth}{c|lll}
\centering\textbf{Framework} & Dynet &  TensorFlow & Theano \\  \hline
\specialcell{matrix multiply \\(\texttt{magma\_lds128...})} & 29.64\%  &  68.87\% & 49.90\% \\
CUDA memset & 40.13\% & 0.00\% & 0.24\% \\
\end{tabularx}

@@

@@

%% BOX 2
\headerbox{Conclusions and Recommendations}{name=results,column=2,row=0.69, span=1}{

Many tradeoffs to consider when selecting a framework: none of them
win across the board.
\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
    \item Performance: see above!
    \item Simple or complicated installation?
    \item Is it well-documented?
    \item Is there a steep learning curve?
    \item Are there convenient built-ins?
    \item How difficult is it to debug computation graphs?
\end{itemize}
}

>>>>

\documentclass[paperwidth=118cm,paperheight=84cm,portrait,margin=8em,fontscale=0.3]{baposter}
%\usepackage{acl-hlt2011}
%84 cm wide x 118 cm high
\usepackage{times}
\usepackage{svg}
\usepackage{color}
\usepackage{multirow}
\usepackage{latexsym}
\usepackage{amsmath,amssymb}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{wrapfig}

@@

\bgroup
\def\arraystretch{1.1}
\setlength\tabcolsep{5mm}
\begin{tabular}{c|ccc}
Time					& Dynet 		& TensorFlow 	& Theano \\ \hline
Convergence		& 26h10m 		& 35h25m 			& (TBD)\\
Train epoch 		& 2h20m		& 6h57m 			& 6h35m \\
Test epoch 		& 3m4s			& 7m45s 			& 24m \\
Train batch 		& 1s 				& 5s 					& 1s \\
Test batch 			& $<$1s 		& $<$1s 			& $<$1s \\
\end{tabular}
\egroup
\vspace{5pt}
}

@@

\begin{center}
\textbf{Time spent in various functions}
\end{center}

@@

\begin{tabularx}{\textwidth}{c|lll}
\centering\textbf{Function} & Dynet &  TensorFlow & Theano \\  
\hline
\specialcell{matrix multiply \\(\texttt{magma\_lds128...})} & 29.64\%  &  68.87\% & 49.90\% \\
\hline
CUDA memset & 40.13\% & 0.00\% & 0.24\% \\
\end{tabularx}

@@

\begin{center}
\textbf{Function-level GPU metrics}
\end{center}

@@

%% BOX 2
\headerbox{Conclusions and Recommendations}{name=results,column=2,row=0.68, span=1}{

\begin{wrapfigure}{r}{0.4\textwidth}
\includegraphics[scale=.4]{../paper/graphics/tensorflowGraph.png}
\end{wrapfigure}

Many tradeoffs to consider when selecting a framework: none of the tested frameworks
win or lose across the board.

\begin{itemize}\addtolength{\itemsep}{-0.5\baselineskip}
    \item Performance: see above!
    \item Simple or complicated installation?
    \item Is it well-documented?
    \item Is there a steep learning curve?
    \item Are there convenient built-ins?
    \item How difficult is it to debug computation graphs?
\end{itemize}

\vspace{0.0mm}
